Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/projectrapport.tex

\chapter{Functional requirements}
\section{DEVS Formalisms}
\section{Single core}
The single core implementations follow exactly the runtime behaviour shown by the PyPDEVS simulator. We've chosen to emulate the Select() function with an integer priority value the user can set. This saves 1 virtual function call per transition and can quite easily be optimized by the compiler since it remains constant.
\subsection{DirectConnect}
%TODO Stijn/Matthijs Directconnect : what is rootmodel, only atomics in core.
\subsection{Dynamic Structured}
Only the removal/addition of connections is currently supported. Unlike the PyPDEVS, we will try to keep a removed model intact when it is removed from the simulation.
\subsection{Parallel}
\subsubsection{Optimistic}
Optimistic time synchronization requires an implementation of timewarp, and more extensive locking than would be required for conservative. The GVT algorithm (Mattern \cite{Mattern}) runs on a separate thread from the simulation kernel threads, so care must be taken that they don't deadlock, but don't race either.
\subsubsection{Conservative}
Conservative time synchronization is still under development.

>>>>

\chapter{Functional requirements}
\section{DEVS Formalisms}
\section{Single core}
The single core implementations follow exactly the runtime behaviour shown by the PyPDEVS simulator. We've chosen to emulate the Select() function with an integer priority value the user can set. This saves 1 virtual function call per transition and can quite easily be optimized by the compiler since it remains constant.
\subsection{DirectConnect}
The directConnect algorithm has gone relatively unchanged from its implementation in PyPDEVS, though the role of the RootDEVS class has been simplified somewhat. Its main function has been reduced to executing directConnect and then storing the resulting list of connected atomic models.
\subsection{Dynamic Structured}
Only the removal/addition of connections is currently supported. Unlike the PyPDEVS, we will try to keep a removed model intact when it is removed from the simulation.
\subsection{Parallel}
\subsubsection{Optimistic}
Optimistic time synchronization requires an implementation of timewarp, and more extensive locking than would be required for conservative. The GVT algorithm (Mattern \cite{Mattern}) runs on a separate thread from the simulation kernel threads, so care must be taken that they don't deadlock, but don't race either.
\subsubsection{Conservative}
Conservative time synchronization is still under development.
